---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# rmarkdown-website

<!-- badges: start -->
<!-- badges: end -->

a template for creating a website in R Markdown

## Set up hosting (once)

1. Turn on hosting via GitHub Pages
    1. Settings -> GitHub Pages -> Source -> select "master branch `/docs` folder"
1. View your website at given URL
    1. In case: (https://sds236-s20.github.io/rmarkdown-website/)

## Maintainence

1. Change content as necessary
    1. Modify existing `.Rmd` files
    1. Add new files as necessary
    1. Update `_site.yml` as necessary
1. Render entire site by running:

```{r, eval=FALSE}
rmarkdown::render_site("www")
```

1. Commit and push changes. 
    1. Make sure to commit changes to **both** the `.Rmd` files in `www/` **and** the `.html` files in `docs/`

## Resources

- [R Markdown websites](https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html)
- [Bootstrap 3.3 components](https://getbootstrap.com/docs/3.3/components/)
- [Bootswatch themes](https://bootswatch.com/3/)
- [Font Awesome icons](https://fontawesome.com/icons?d=gallery&m=free)

